### 2024-09-20 article_codes.qmd
Add buildigns per WUI (and rerun after cleaning cache!)

  r <- .x
  # Identify levels (1 = Interface, 2 = Intermix)
  df_lev <- data.frame(id = 0:2, wui_class = c("No_wui", "Interface", "Intermix"))
  df_lev_lst <- replicate(nlyr(r), df_lev, simplify = FALSE)
  levels(r) <- df_lev_lst
  # Add colour table 
  df_col <- data.frame(id = 0:2, col = c("lightgrey", "#FF6633", "#003366"))
  df_col_lst <- replicate(nlyr(r), df_col, simplify = FALSE)
  coltab(r) <- df_col_lst

>>>>

  r <- .x
  # Identify levels (1 = Interface, 2 = Intermix)
  df_lev <- data.frame(id = 0:2, wui_class = c("No_wui", "Interface", "Intermix"))
  df_lev_lst <- replicate(nlyr(r), df_lev, simplify = FALSE)
  levels(r) <- df_lev_lst
  # Add colour table 
  df_col <- data.frame(id = 0:2, col = c("#FAFAFA", "#FF6633", "#003366"))
  df_col_lst <- replicate(nlyr(r), df_col, simplify = FALSE)
  coltab(r) <- df_col_lst
